biological data preperation

### 2019-01-14 src/biological_data_prep.Rmd
depth missing values

>>>>

This is interesting...
chl and o2 are missing the same number of points - they come from the biomer dataset; salinity and temp come from glorys and have different values.

I wonder how many of these points represent the same lat-long-depth... need to subset where chl_depth OR o2_depth OR salinity_depth OR temp_depth == OR These columns are not together

```{r}
presence_wdepth2 <-  presence_wdepth[!(is.na(presence_wdepth$chl_depth) & is.na(presence_wdepth$o2_depth) & is.na(presence_wdepth$salinity_depth) & is.na(presence_wdepth$temp_depth)) , ]
nrow(presence_wdepth2)
```
